Sequence variability as the main determinant of sequence-structure relationships

### 2015-05-25 manuscript/manuscript.tex
More figures

\title{Sequence divergence as the main determinant of sequence-structure relationships}
\author{Amir Shahmoradi$^{1*}$, Eleisha L. Jackson$^2$, Claus O. Wilke$^2$}
\begin{document}

@@

    \begin{figure}[H]
            \centerline{\includegraphics[width=4in]{mean_entropy_cn_cor.pdf}}     
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

    \begin{figure}[H]
            \centerline{\includegraphics[width=4in]{var_entropy_cn_cor.pdf}}
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

    \begin{figure}[H]
            \centerline{\includegraphics[width=4in]{mean_entropy_wcn_cor.pdf}}
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

    \begin{figure}[H]
            \centerline{\includegraphics[width=4in]{var_entropy_wcn_cor.pdf}}
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

    \begin{figure}[H]
            \centerline{\includegraphics[width=4in]{mean_entropy_rsa_cor.pdf}}
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

    \begin{figure}[H]
            \centerline{\includegraphics[width=4in]{var_entropy_rsa_cor.pdf}}
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

NEED THE RATE4SITE FIGURES

>>>>

\title{Sequence variability as the main determinant of sequence-structure relationships}
\author{Amir Shahmoradi$^{1*}$, Eleisha L. Jackson$^2$, Claus O. Wilke$^2$}
\begin{document}

@@

    \begin{figure}[H]
            \centerline{\includegraphics[width=7.5in]{entropy_cn_cor.pdf}}     
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

    \begin{figure}[H]
            \centerline{\includegraphics[width=7.5in]{entropy_wcn_cor.pdf}}     
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

    \begin{figure}[H]
            \centerline{\includegraphics[width=7.5in]{entropy_rsa_cor.pdf}}     
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

        \begin{figure}[H]
            \centerline{\includegraphics[width=7.5in]{rate_cor.pdf}}     
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

            \begin{figure}[H]
            \centerline{\includegraphics[width=5.0in]{var_rate_rsa_cor.pdf}}     
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

        \begin{figure}[H]
            \centerline{\includegraphics[width=5.0in]{var_entropy_rate_cor.pdf}}     
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}
